Tabular Constraint Learning

### 2016-05-02 Paper/ECAI/tabular.tex
Comments

\newcommand{\tcl}{Tabular Constraint Learning}
\newcommand{\ctl}{Condensed Tabular Constraint Learning}
\section{Approach to Tabular Constraint Learning}
\sergey{Luc wants this to be more intuitive, should we just add some examples here to make it easier to follow and refer to the running example?}
This section will describe our approach to \tcl.
Our algorithm reasons on the level of groups and vectors on the data and assumes that these are provided.
Often, however, this not the case and a possible approach is to extract the groups from the CSV file directly.
This requires discovering \textit{tables} and \textit{groups}.
Our implementation offers automated procedures for both steps.

\subsection{Table and group detection}
We chose to implement a naive approach to extract tables as the detection of tables and headers from data is a complex task on its own (\cite{header}) and a sophisticated implementation goes beyond the scope of this paper.
Our approach first detects rectangular collections of data.
It then attempts to identify the header by looking at the type of the first row.
If this row consists only of textual entries, the row is expected to be the header and is removed, if not, the same procedure is applied on the first column.
We suggest to provide tables in general, for well formated data, however, the user will not have to specify tables manually.

>>>>

\newcommand{\tcl}{Tabular Constraint Learning}
\newcommand{\ctl}{Condensed Tabular Constraint Learning}
\section{Approach to Tabular Constraint Learning}
% \sergey{Luc wants this to be more intuitive, should we just add some examples here to make it easier to follow and refer to the running example?}
This section will describe our approach to \tcl.
Our algorithm reasons on the level of groups and vectors on the data and assumes that these are provided.
Often, however, this not the case and a possible approach is to extract the groups from the CSV file directly.
This requires discovering \textit{tables} and \textit{groups}.
Our implementation offers automated procedures for both steps.

\subsection{Table and group detection}
\samuel{Is an example needed? I find no because it is not our main concern but open for discussion}
We chose to implement a naive approach to extract tables as the detection of tables and headers from data is a complex task on its own (\cite{header}) and a sophisticated implementation goes beyond the scope of this paper.
Our approach first detects rectangular collections of data.
It then attempts to identify the header by looking at the type of the first row.
If this row consists only of textual entries, the row is expected to be the header and is removed, if not, the same procedure is applied on the first column.
We suggest to provide tables in general, for well formated data, however, the user will not have to specify tables manually.
